Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-03 paper.tex
adding text to the abstract

@@

\item \textbf{Boosting} 
Boosting is an ensemble classification algorithm which was first proposed by \citet{schapire1990strength} in \citet{schapire1990strength}. Boosting is based on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called Adaptive Boosting or "Adaboost" for short \cite{FS1997}. Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

>>>>

An important task when publishing a new book is determining an adequate number 
of copies to be printed, but not a excesive number, as the unsold volumes will 
lead to losses.
In this paper, we face the problem of predicting total sales using cost-sensitive
ensemble methods, that can be used as decision-aid tools for publishers, which 
can provide a reliable guidance on the decision process of publishing a book. 
A real dataset including the complete sales data for books published in Spain 
across several years has been used to create forecasting models.
Results show that \emph{EXPLAIN THE RESULTS OBTAINED}.

@@

\item \textbf{Boosting} 
Boosting is an ensemble classification algorithm which was first proposed by \citet{schapire1990strength} in \citet{schapire1990strength}. Boosting is based on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called Adaptive Boosting or ''Adaboost'' for short \cite{FS1997}. Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.
